\documentclass{article}
\usepackage[margin=1in]{geometry}

\begin{document}

\section*{Personal Information}
Name: Filip Dimitrijevic \\
Address: Simrishamnsvägen 15, Stockholm \\
Phone: +46 703 91 17 70 \\
Email: filipdi@kth.se

\section*{Education}
\subsection*{Master of Science in Computer Science and Engineering}
Royal Institute of Technology (KTH), Stockholm \\
Expected Graduation Date: 2027

\subsection*{Technical Preparatory Year}
Royal Institute of Technology (KTH), Stockholm \\
Graduation Date: 2022 \\
- Completed courses in mathematics, physics, chemistry, and computer science.

\subsection*{Medical Doctor's Program}
University of Belgrade, Faculty of Medicine, Belgrade \\
Dates: 2017-2020 \\
- Completed 3 years of the medical program and enrolled in the 4th year.

\section*{Experience}
\subsection*{Business Relations Member}
KTH AI Society, Stockholm \\
Dates: 2022 - Present \\
- Working closely with the event team to spread awareness about artificial intelligence.
- Contacting different companies that research or apply artificial intelligence in their business or organization.

\subsection*{Medical Assistant}
Västra Götalandsregionen, Alingsås \\
Dates: 2020 - 2021 \\
- Provided technical support to employees in a fast-paced, deadline-driven environment.
- Assisted medical doctors and nurses with patient care during the pandemic.
- Measured vital signs, provided daily patient care, performed COVID-testing, and supported nurses in blood testing and surgical wound care.
- Collected health care data and wrote in patient journals.
- Was responsible for in-calls, managing all in-calls for a specific hospital ward during some shifts.

\subsection*{Teacher Assistant}
Academedia AB, Alingsås \\
Dates: 2016 - 2017 \\
- Assisted the teacher responsible for the English course.
- Taught and planned the academic year for 7th to 9th-grade students.
- Was responsible for creating assignments and assessing and grading 150 students.
- Managed activity days by educating a small group of students in film history.

\section*{Skills}
- Proficient in Java
- Have some experience with Python, C++, JavaScript, and HTML.
- Understanding of data structures and algorithms.
- Experience with Git and GitHub.
- Strong problem-solving and analytical skills.

\section*{Activities and Interests}
- Member of the KTH AI Society
- Has worked as a tennis coach for 5 years and has been a member of the tennis club for 10 years.
- Interested in artificial intelligence and machine learning.

\end{document}
